ConocoPhillips2020

### 2020-05-19 CP_2020.Rmd
minor edit to data analysis

```{r}
COP_close <- COP_close %>% select(-"start_day")
start <- which(COP_close$Date == "2020-03-06")
start_day <- as.numeric(1:nrow(COP_close) >= start)
COP_close <- COP_close %>% mutate(start_day = start_day)
COP_close_small <- COP_close[(start-30):(start), ]
dim(COP_close_small)
m_COP_03_09_20 <- lm(Y ~ COP_Close + start_day + GSPC_Close, 
                    data = COP_close_small)
summary(m_COP_03_09_20)
alpha_03_09_20_1 <- summary(m_COP_03_09_20)$coef[3,1:2]
alpha_03_09_20_1 #-10.51414
```

Here is the 5 day shock effect

```{r}
COP_close_small <- COP_close[(start-30):(start+4), ]
dim(COP_close_small)
m_COP_03_09_20 <- lm(Y ~ COP_Close + start_day + GSPC_Close, 
                    data = COP_close_small)
summary(m_COP_03_09_20)
alpha_03_09_20_5 <- summary(m_COP_03_09_20)$coef[3,1:2]
alpha_03_09_20_5 #-5.333522
```

>>>>

```{r}
COP_close <- COP_close %>% select(-"start_day")
start <- which(COP_close$Date == "2020-03-06")
start_day <- as.numeric(1:nrow(COP_close) >= start)
COP_close <- COP_close %>% mutate(start_day = start_day)
COP_close_small <- COP_close[(start-30):(start), ]
dim(COP_close_small)
```

```{r}
m_COP_03_09_20 <- lm(Y ~ COP_Close + start_day + GSPC_Close, 
                    data = COP_close_small)
summary(m_COP_03_09_20)
alpha_03_09_20_1 <- summary(m_COP_03_09_20)$coef[3,1:2]
alpha_03_09_20_1 #-10.51414 (1.62901)
```

```{r}
m_COP_03_09_20 <- lm(Y ~ COP_Close + start_day, data = COP_close_small)
summary(m_COP_03_09_20)
alpha_03_09_20_1_no <- summary(m_COP_03_09_20)$coef[3,1:2]
alpha_03_09_20_1_no #-10.533756 (1.617991)
```

Here is the 5 day shock effect with S&P 500:

```{r}
COP_close_small <- COP_close[(start-30):(start+4), ]
dim(COP_close_small)
m_COP_03_09_20 <- lm(Y ~ COP_Close + start_day + GSPC_Close, 
                    data = COP_close_small)
summary(m_COP_03_09_20)
alpha_03_09_20_5 <- summary(m_COP_03_09_20)$coef[3,1:2]
alpha_03_09_20_5 #-5.333522 (2.077089)
```

Here is the 5 day shock effect without S&P 500:

```{r}
m_COP_03_09_20 <- lm(Y ~ COP_Close + start_day, data = COP_close_small)
summary(m_COP_03_09_20)
alpha_03_09_20_5_no <- summary(m_COP_03_09_20)$coef[3,1:2]
alpha_03_09_20_5_no #-5.314242 (2.031455)
```
